---
title: "Pitching News Story Template"
author: "Isabelle Farina"
date: "2026-06-01"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
library(tidyverse)
```
Story Pitch Template: Your Name, Contact Information, Date Isabelle
Farina,
[isabellefarina546\@gmail.com](mailto:isabellefarina546@gmail.com){.email},
6/1/2026

### In two sentences, what is this story about?

New Jersey is consistently recorded as [one of the most expensive states
to live
in](https://worldpopulationreview.com/state-rankings/cost-of-living-index-by-state),
and not just because of its proximity to New York City, exuberant
restaurant scene and luxurious beaches. In fact, most of the benefits of
living in the armpit of America come later in life with social security
benefits. In all 22 counties of the state, the Social Security
Administration receives the most federal spending. Why is social
security such a high priority in New Jersey, and do locals think it's
worth it?

### In one sentence, why tell this story NOW?

This story is relevant because there have been [significant
changes](https://www.aarp.org/social-security/biggest-2026-changes/) in
the last year to what social security entails, and people need clarity
on what this means.

### Who is your target audience?

- folks of benefit-earning age who have been paying social security
  taxes in NJ their whole lives and want to ensure they rightfully
  receive their benefits
- younger families who want to know if it is worth it in the long run to
  live in a state as expensive as NJ
- disabled/financially insecure people who currently benefit from social
  security

### Three people you can interview for this story

- An NJ official who is involved and knowledgeable on NJ’s budget and
  federal spending on Social Security Administration
  - Security Administration Governor Mikie Sherrell, Phone: (609)
    292-6000
  - Regional Commissioner of Social Security Administration for NJ/NY
    Region Raymond Egan
  - New Jersey State Treasurer Aaron Binder (Office number:
    609-292-6748)
- A local resident currently receiving and dependent on social security
  benefits
  - Do they purposely live in NJ?
  - How have their benefits changed recently? Why should states value
    social security?
- A local resident who pays taxes
  - Are they aware of NJ’s prioritization of social security? do they
    know what benefits they are entitled to?

### Potential impact

Nationally, social security is experiencing drastic changes, and it is
important to narrow our focus on how these adjustments affect New
Jersey, along with how the state’s high federal spending on the Social
Security Association mitigates or worsens these effects. If it is proven
this priority is worth it, it may inspire other states to follow suit,
but if it is not, New Jerseyans can advocate for change to adjust
spending. Additionally, if people are aware of what they are entitled to
through social security and what they like and dislike about the system,
they will have the necessary knowledge to vote on it.

### What are three things that surprised or interested you about this story?

I was not aware of how much social security encompasses. It goes far
beyond old people receiving benefits, and includes things like
Supplemental Security Income. Additionally, I was not fully aware of how
much change social security is undergoing recently. I want to be able to
connect the trend of every NJ county having SSA as its number one agency
for federal spending to the national changes.

### Context: Summarize any previous coverage + What other information do you need to gather?

[Social Security benefit cuts could be coming — and there’s an actual
date
attached](https://www.nj.com/news/2026/04/social-security-benefit-cuts-could-be-coming-and-theres-an-actual-date-attached.html)

- The Congressional Budget Office is saying that Social Security could
  run out of money a year sooner in 2032 due to a provision in the One
  Big Beautiful Bill Act. To address this budget shortfall, there are
  proposals to make cuts to Social Security.

  - How does this intersect with NJ’s federal spending?

[Social Security’s proposed rule change could cut benefits for nearly
400K disabled people. Here’s
why](https://www.nj.com/news/2026/05/social-securitys-proposed-rule-change-could-cut-benefits-for-nearly-400k-disabled-people-heres-why.html)

- The Social Security Administration would remove Supplemental Nutrition
  Assistance Program (SNAP) benefits as a qualification to receive
  Supplemental Security Income (SSI) and tighten the qualifications for
  what is deemed a “public assistance household,” according to an
  Executive Order submission currently under review.

  - What does this mean for NJ, a state that directs most of its federal
    spending towards the Social Security Administration?

[Social Security COLA 2027 projection released, and the amount may
surprise
you](https://www.nj.com/news/2026/04/social-security-cola-2027-projection-released-and-the-amount-may-surprise-you.html)

- According to the Senior Citizens League, the 2027 cost of living
  assessment will remain flat at 2.8%, the same as it was in 2026.

  - How do citizens feel about this?

### Photos, video, graphics - How will you make this story visual?

- graphic illustrating what social security benefits includes –
  basically what are SS benefits
- comparison of how much federal spending on SSA in NJ vs other states

### Estimated delivery

In order to conduct thorough interviews with several local residents who
bring different perspectives to the story, interview a knowledgeable
expert on NJ finances who may be difficult to contact, and compile data
into pleasing visualizations, I anticipate this assignment to take me
two to three weeks.

# Total spending by county for Social Security Administration

```{r}
federal_spending <- read_csv("data/federal spending by county 2020-2024.csv")
```
```{r}
nj_spending <- federal_spending |>
  filter(state_nm == "NEW JERSEY")
```


```{r}
nj_spending |> 
group_by(cty_name) |> 
  filter(agency=="Social Security Administration") |>
  summarize(
    total_spent = sum(spending_total, na.rm = TRUE), 
    states_spending = sum(spending_total[!is.na(state_nm)], na.rm = TRUE)) |> 
   mutate(`total_spent_$` = scales::dollar(total_spent / 1e9, suffix = "B", accuracy = 0.01)) |> 
  arrange(desc(total_spent))


```
