---
title: "Pitching News Story Template"
author: "Isabelle Farina"
date: "2026-06-01"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
execute:
  warning: false
---

```{r}
library(tidyverse)
```

Isabelle
Farina,[isabellefarina546\@gmail.com](mailto:isabellefarina546@gmail.com){.email},
6/6/2026

<iframe title="Federal Spending on Social Security Administration in USA per capita" aria-label="Choropleth map" id="datawrapper-chart-bkUG5" src="https://datawrapper.dwcdn.net/bkUG5/1/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height data-external="1">

</iframe>

```{=html}
<script type="text/javascript">(function(){function e(){window.addEventListener(`message`,function(e){if(e.data[`datawrapper-height`]!==void 0){var t=document.querySelectorAll(`iframe`);for(var n in e.data[`datawrapper-height`])for(var r=0,i;i=t[r];r++)if(i.contentWindow===e.source){var a=e.data[`datawrapper-height`][n]+`px`;i.style.height=a}}})}e()})();</script>
```

### What is this story about?

New Jersey is consistently [one of the most expensive states to live
in](https://worldpopulationreview.com/state-rankings/cost-of-living-index-by-state),
and not just because of its proximity to New York City, delicious
restaurants and luxurious beaches. In fact, most of the benefits of
living in the armpit of America come later in life with social security
benefits.

**According to the** **Congressional Budget Office,** Social Security is
less than [seven years away from insolvency](#0). If that occurs, there
**could be a** a 24% across-the-board benefit cut. In all 21 counties of
New Jersey, the Social Security Administration **provides** the most
federal spending. This would make potential cuts to benefits all the
more stinging.

**This story proposal examines what a reduction in Social Security
spending would look like in each county in New Jersey.**

### Federal Spending on Social Security Administration By State

```{r}
federal_spending <- read_csv("https://raw.githubusercontent.com/djnf-data-2026/master/refs/heads/main/data/federal_spending_by_county_2020%202024%20rob_0416_v2.csv")
```

```{r}
nj_spending <- federal_spending |>
  filter(state_nm == "NEW JERSEY")
```

This table demonstrates the top 15 states with the most federal spending
on the Social Security Administration. New Jersey is ranked number 11
with \$180.06 billion **from 2020-2024**. While this is significantly
less than California's \$620.75 billion, it is pretty high for a small
state.

```{r}
state_spending <- federal_spending %>%
group_by(state_nm) |> 
  filter(agency=="Social Security Administration") |>
  summarize(
    total_spent = sum(spending_total, na.rm = TRUE)) |>
   mutate(`total_spent_$` = scales::dollar(total_spent / 1e9, suffix = "B", accuracy = 0.01)) |> 
  arrange(desc(total_spent))
print(state_spending, n = 15)

```

However, it is important to analyze spending per capita. Per captia
means dividing the total amount by the number of individuals in a
population, allowing for fair comparisons across groups of different
sizes. New Jersey is actually ranked 33 for SSA spending per capita.
Nonetheless, New Jersey's large population and high sums spent on SSA
make this a variable worth analyzing.

<iframe title="Ranking SSA Spending Per Capita Per State" aria-label="Table" id="datawrapper-chart-bUUu4" src="https://datawrapper.dwcdn.net/bUUu4/1/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height data-external="1">

</iframe>

```{=html}
<script type="text/javascript">(function(){function e(){window.addEventListener(`message`,function(e){if(e.data[`datawrapper-height`]!==void 0){var t=document.querySelectorAll(`iframe`);for(var n in e.data[`datawrapper-height`])for(var r=0,i;i=t[r];r++)if(i.contentWindow===e.source){var a=e.data[`datawrapper-height`][n]+`px`;i.style.height=a}}})}e()})();</script>
```

spening per capita

```{r}
pop <- read_csv("../data/population_inc_2024.csv") %>% 
  mutate(state1 = str_to_upper(NAME)) %>% 
  select(state1, estimate)

#add population
state_spending1 <- state_spending %>% 
  inner_join(pop, by=c("state_nm" = "state1")) %>% 
  rename(population = estimate) %>% 
  mutate(spending_per_capita = (total_spent/population)) %>% 
  arrange(desc(spending_per_capita)) %>% 
  mutate(rank = row_number())

write_csv(state_spending1,("state_spending1.csv"))

```

### In one sentence, why tell this story NOW?

This story is relevant because there have been [significant
changes](https://www.aarp.org/social-security/biggest-2026-changes/) in
the last year to what Social Security entails, and people need clarity
on what this means, especially if even larger cuts are coming in the
near future.

### Who is your target audience?

- Folks of benefit-earning age who have been paying Social Security
  taxes in NJ their whole lives and want to ensure they rightfully
  receive their benefits
- Younger families who want to know if it is worth it in the long run to
  live in a state as expensive as NJ
- Disabled/financially insecure people who currently benefit from Social
  Security

### Three people you can interview for this story

- An NJ official who is involved and knowledgeable on NJ’s budget and
  federal spending on Social Security Administration
  - New Jersey Governor Mikie Sherrill, Phone: (609) 292-6000
  - Regional Commissioner of Social Security Administration for NJ/NY
    Region Raymond Egan
  - Director of Economic Justice and Public Benefits Clinic at Rutgers
    University Jon Dubin
    - How will Supplemental Security Income (SSI) be impacted? Economic
      justice?
- A local resident currently receiving and dependent on Social Security
  benefits
  - Do they purposely live in NJ?
  - How have their benefits changed recently? Why should states value
    Social Security?
- A local resident who pays taxes
  - Are they aware of NJ’s contribution to Social Security? Do they know
    what benefits they are entitled to?

### Potential impact

Nationally, Social Security is experiencing drastic changes, and it is
important to narrow our focus on how these adjustments affect New
Jersey, along with how the state’s high federal spending on the Social
Security Administration mitigates or worsens these effects.

```{r}
county_spending <- nj_spending |> 
group_by(cty_name) |> 
  filter(agency=="Social Security Administration") |>
  summarize(
    total_spent = sum(spending_total, na.rm = TRUE)) |>
   mutate(`total_spent_$` = scales::dollar(total_spent / 1e9, suffix = "B", accuracy = 0.01)) |> 
  arrange(desc(total_spent))
print(county_spending, n = 21)

```

This is the federal spending on the Social Security Administration in
the 21 counties of New Jersey in order of most to least populous. Bergen
County has the most spending with \$18.83 billion and Salem County has
the least with \$1.64 billion.

### What are three things that surprised or interested you about this story?

I was not aware of how much Social Security encompasses. It goes far
beyond old people receiving benefits, and includes things like
Supplemental Security Income. In New Jersey, Social Security administers
the State supplement of the Federal SSI benefit with additional
payments. Additionally, I was not fully aware of how much change Social
Security is undergoing recently. I want to be able to connect the trend
of every NJ county having SSA as its number one agency for federal
spending to the national changes.

### Context: Summarize any previous coverage + What other information do you need to gather?

[Social Security benefit cuts could be coming — and there’s an actual
date
attached](https://www.nj.com/news/2026/04/social-security-benefit-cuts-could-be-coming-and-theres-an-actual-date-attached.html)

- The Congressional Budget Office is saying that Social Security could
  run out of money a year sooner in 2032 due to a provision in the One
  Big Beautiful Bill Act. To address this budget shortfall, there are
  proposals to make cuts to Social Security.

## How does this intersect with NJ’s federal spending?

This graph demonstrates how each county's spending on Social Security
Administration would be reduced per capita if the 24% cut was put in
place. In the visualization, the red represents the reduction, while the
blue represents what would remain.

```{r}
nj <- read_csv("../data/nj_update.csv")
nj_county_pop <- nj |> select(cty_name, county_pop) |> distinct()
```

```{r}

county_sums <- county_spending |>
  inner_join(nj_county_pop)

per_capita <- county_sums |> mutate(per_capita=total_spent/county_pop)

```

```{r}
per_capita <- per_capita |> 
  mutate(spending_reduce=total_spent-(total_spent * 0.24))
```

```{r}
options(scipen=999)
ggplot(per_capita,aes(x = cty_name)) + 
  geom_col(aes(y = total_spent), fill = "red") +
    geom_col(aes(y = spending_reduce), fill = "blue") +
  theme(axis.text.x=element_text(angle=90)) +
 scale_y_continuous(labels = scales::dollar) +
  #geom_text(aes(label = scales::percent(percent)), size = 4) +
  labs(title = " Reduction in Social Security Spending By County",
       subtitle = "Potential 24% cut",
       caption = "If Social Security becomes insolvent, this is the effect on NJ counties",
       y="",
       x="County")
```

[Social Security’s proposed rule change could cut benefits for nearly
400K disabled people. Here’s
why](https://www.nj.com/news/2026/05/social-securitys-proposed-rule-change-could-cut-benefits-for-nearly-400k-disabled-people-heres-why.html)

- The Social Security Administration would remove Supplemental Nutrition
  Assistance Program (SNAP) benefits as a qualification to receive
  Supplemental Security Income (SSI) and tighten the qualifications for
  what is deemed a “public assistance household,” according to an
  Executive Order submission currently under review.

  - What does this mean for NJ, a state that directs most of its federal
    spending towards the Social Security Administration?

[Social Security COLA 2027 projection released, and the amount may
surprise
you](https://www.nj.com/news/2026/04/social-security-cola-2027-projection-released-and-the-amount-may-surprise-you.html)

- According to the Senior Citizens League, the 2027 cost of living
  assessment will remain flat at 2.8%, the same as it was in 2026.

  - How do citizens feel about this?

# Total Spending By County for Social Security Administration

This interactive map demonstrates all 21 counties and their per capita
receipts for Social Security. Cape May County has the most with
\$35,065.68, while Hudson County has the least with \$12,359.68.

```{r}
federal_spending <- read_csv("../data/federal spending by county 2020-2024.csv")
```

```{r}
nj_spending <- federal_spending |>
  filter(state_nm == "NEW JERSEY")
```

#Population

```{r}
#DONT NEED THIS LINE - ALREADY IMPORTED IT
#nj <- read_csv("../data/nj_update.csv")
nj_county_pop <- nj |> select(cty_name, county_pop) |> distinct()
```

```{r}
per_capita <- per_capita |> 
  mutate(spending_reduce=total_spent-(total_spent * 0.24))
```

```{r}

county_sums <- county_spending |>
  inner_join(nj_county_pop)

per_capita <- county_sums |> mutate(per_capita=total_spent/county_pop)

```

<iframe title="Federal Spending on Social Security Administration in NJ per capita" aria-label="Choropleth map" id="datawrapper-chart-PpmLo" src="https://datawrapper.dwcdn.net/PpmLo/1/" scrolling="no" frameborder="0" style="width: 0; min-width: 100% !important; border: none;" height data-external="1">

</iframe>

```{=html}
<script type="text/javascript">(function(){function e(){window.addEventListener(`message`,function(e){if(e.data[`datawrapper-height`]!==void 0){var t=document.querySelectorAll(`iframe`);for(var n in e.data[`datawrapper-height`])for(var r=0,i;i=t[r];r++)if(i.contentWindow===e.source){var a=e.data[`datawrapper-height`][n]+`px`;i.style.height=a}}})}e()})();</script>
```

```{r}
per_capita <- per_capita |> 
  mutate(spending_reduce=total_spent-(total_spent * 0.24))
```

### Potential Holes

It is important to acknowledge that census data is ever-changing. Data
is an approximation, and no data-set is completely fixed. Additionally,
this spending information is from 2020-2024, meaning the affect of the
potential cut will change as the spending changes year to year.

### Impacted Businesses

One company relevant to changes to Social Security benefits would be the
medical company Johnson & Johnson, which has a prescription-drug
benefits program. However, [several cases have been filed in various
state courts of New
Jersey](https://www.sec.gov/Archives/edgar/data/200406/000020040626000016/jnj-20251228.htm),
specifically multi-county litigation in Bergen County. The cases are the
result of using ELMIRON, a prescription medication for the relief of
bladder pain. In addition to legal updates, medical companies like
Johnson & Johnson are important to watch amidst changes to Social
Security.

### Estimated delivery

In order to conduct thorough interviews with several local residents who
bring different perspectives to the story, interview a knowledgeable
expert on NJ finances who may be difficult to contact and compile data
into pleasing visualizations, I anticipate this assignment to take me
two to three weeks.
